New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-07-30 coupling.tex
Changes for arboreal coupling

System of equations \eqref{eq:bt2} is overdetermined because there are $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.  Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns. This principle underlies arboreal coupling methods.

@@

@@

More generally, to obtain a regular system of equations for  any of $K$ , it is necessary and sufficient that the tree formed by edges for which we include equations from Bradley-Terry system is  a spanning tree. Note that any arboreal method is non-canonical, because there is no natural way to choose a spanning tree in a complete graph. In fact, a stronger statement is true -- no arboreal method is symmetric. 
To see that, consider the action of the transposition of a vertex $v$ of degree one and another vertex $v'$ of degree $>1$ in a spanning tree. The results of coupling involves different number of equations for classes $C_v$ and $C_v'$ which is a contradiction.
%However, we will see in Section \ref{sec:bc2} that by ``averaging'' several stars we can obtain a canonical

>>>>

System of equations \eqref{eq:bt2} is overdetermined because there are $K$ unknowns and $\binom{K}{2}$ equations together with the requirement that the total sum of predicted probabilities is one.  Given an overdetermined system of equations, a common approach is to select a minimal subset of equations needed to solve for the unknowns. This principle underlies arboreal coupling methods.

@@

It is useful to consider the graph on $K$ vertices, where vertices correspond to the classes and edges to the selected equations. It cannot have a cycle, otherwise the subsystem of Bradley-Terry equations would be overdetermined for unknowns representing the vertices of the cycle. Therefore it has to be a spanning tree.

@@

%More generally, to obtain a regular system of equations for  any of $K$ , it is necessary and sufficient that the tree formed by edges for which we include equations from Bradley-Terry system is  a spanning tree.

Note that any arboreal method is non-canonical, because there is no natural way to choose a spanning tree in a complete graph. 
%In fact, a stronger statement is true -- no arboreal method is symmetric. 
In fact, a stronger statement is true.
\begin{prop}
No arboreal method is symmetric. 
\end{prop}
\begin{proof}
First note that any spanning tree has a vertex $v$ of degree one and another vertex $v'$ of degree $>1$. Now consider the transposition $\sigma$ exchanging  vertices $v$  and $v'$. Since coupling involves different number of equations for classes $C_v$ and $C_{v'}$ the required condition \eqref{eq:symmetry} cannot hold for $\sigma$.
\end{proof}
%However, we will see in Section \ref{sec:bc2} that by ``averaging'' several stars we can obtain a canonical
